Plots

### 2024-11-23 Archive/Plots.Rmd
Plot 5 mostly done, needs more work

venue_plot_no2022 <- ggplot(venue_effects_no2022,
                                   aes(x = rownames(venue_effects_no2022),
                                       y = `Effect Value`)) +
  geom_point() + 
  labs(x = "Venue", y = "Venue Effect") +
  scale_y_continuous(limits = c(-0.15, 0.1))
```
### Now we combine for final product
```{r}
library(gridExtra)
venue_effects_combined <- grid.arrange(venue_plot,
                                       venue_plot_no2022, ncol = 1)
ggsave(filename = "ComparisonOfVenueEffects.pdf", path = "../Manuscript",
       plot=venue_effects_combined, height = 6.5, width = 7)
```
# Figure 4
```{r}

pdf(file = "../Manuscript/GGResiduals.pdf", height = 4, width = 6)
qq_conf_plot(residuals(gg3b), dparams = list(mean = 0, sd = 1))
dev.off()
```

# Figure 5
```{r}
sim_time <- function(model, RxnTime) {
  simfit <- function(model, n = 10000000) {

    sd_Venue <- model$mu.coefSmo[[1]]$sigb
    sd_Venue_heat <- model$sigma.coefSmo[[1]]$sigb[1]

@@

    x <- rGG(n, mu = mu, sigma = sigma, nu = nu)
    x
  }
  x <- simfit(model)
  plot(density(x), xlim = c(0, 0.3), main = "", xlab = "")
  curve(dGG(x, mu = exp(model$mu.coefficients[1]),
            sigma = exp(model$sigma.coefficients[1]),
            nu = model$nu.coefficients[1]),0, 0.3, add = TRUE, col = "blue",
        main = "", xlab = "")
}
pdf(file = "../Manuscript/GGDensity.pdf", height = 4, width = 6)
sim_time(gg3b, 0.1)
dev.off()
```

>>>>

venue_plot_no2022 <- ggplot(venue_effects_no2022,
                                   aes(x = rownames(venue_effects_no2022),
                                       y = `Effect Value`)) +
  geom_point() + 
  labs(x = "Venue", y = "Venue Effect") +
  scale_y_continuous(limits = c(-0.15, 0.1))
```
### Now we combine for final product
```{r}
library(gridExtra)
venue_effects_combined <- grid.arrange(venue_plot,
                                       venue_plot_no2022, ncol = 1)
ggsave(filename = "ComparisonOfVenueEffects.pdf", path = "../Manuscript",
       plot=venue_effects_combined, height = 6.5, width = 7)
```

# Figure 4
Calculation of curve
```{r}
simfit <- function(model, n = 10000000) {
    set.seed(1)
    sd_Venue <- model$mu.coefSmo[[1]]$sigb
    sd_Venue_heat <- model$sigma.coefSmo[[1]]$sigb[1]

@@

    rGG(n, mu = mu, sigma = sigma, nu = nu)
}
samplefit <- simfit(gg3b)
samplefit0 <- samplefit[1:1000000]
kernfit <- density(samplefit0)

Now we make the density graph
```{r}
make_graph <- function(n = 1000000){
  plot(density(samplefit, n=n), xlim = c(0, 0.3), ylim = c(0, 25), xlab = "",
     main = "")
  curve(dGG(x, mu = exp(gg3b$mu.coefficients[1]),
          sigma = exp(gg3b$sigma.coefficients[1]),
          nu = gg3b$nu.coefficients[1]),0, 0.3, add = TRUE, col = "blue",
      main = "", xlab = "", ylab = "")
}
density_plot <- make_graph(1000000)
```

And combine it with the residuals
```{r}
library(gridExtra)
resid_plot <- qq_conf_plot(residuals(gg3b), dparams = list(mean = 0, sd = 1))
density_plot <- grid.arrange(resid_plot, density_plot, ncol = 2)
ggsave(filename = "ResidualsDensityPlot", path = "../Manuscript",
       plot=resid_density, height = 4, width = 8)
```
